Liveness-Based Garbage Collection for Lazy Languages

### 2016-04-14 paper/cfg-to-nfa.tex
inlined nfa and dfa

\newcommand{\nfaD}{%
  \scalebox{.5}{\psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
    \begin{pspicture}(0,-3)(50,12)
      \putnode{t0}{origin}{5}{0}{} 
      \putnode{t1}{t0}{15}{0}{\pscirclebox{\mbox{\ \ \ \      }}}
      \hspace{5mm} 
      \putnode{t2}{t1}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}} 
      \psset{arrows=->} \ncline{t0}{t1} 
      \ncline{t1}{t2} 
      \putnode{l0}{t1}{7}{2}{\clazy} \nccurve[angleA=45, angleB=135, 
        ncurv=4, nodesep=-1]{t1}{t1} 
      \putnode{l1}{t1}{0}{8}{\acdr, \clazy} \nccurve[angleA=45,
        angleB=135, ncurv=3, nodesep=-1]{t2}{t2} 
      \putnode{l2}{t2}{0}{8}{\clazy}
    \end{pspicture}
}}
\newcommand{\dfaD}{%
    \psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
    \begin{pspicture}(0,-3)(30,12)
      \putnode{t0}{origin}{5}{0}{\var{\Df{\length}{1}}} \putnode{t1}{t0}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \
      }}}     \psset{arrows=->}    \ncline{t0}{t1}     \nccurve[angleA=45,
        angleB=135,                                                 ncurv=3,
        nodesep=-1]{t1}{t1} \putnode{l1}{t1}{0}{8}{\acdr}
    \end{pspicture}
}
The  NFA for \var{\Df{\length}{1}} is 
\nfaD\ and the final DFA is \dfaD.
This  expectedly says  that
for  a  demand  $\sigma_{\length}$,   the  liveness  of  the  argument
of \length\ is $\acdr^{*}$ (the spine of the list is traversed).

>>>>

\newcommand{\nfaD}{%
  \scalebox{.7}{
    \psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
    \begin{pspicture}(2,-2)(30,10)
      \putnode{t0}{origin}{2}{-1}{} 
      \putnode{t1}{t0}{8}{0}{\pscirclebox{\mbox{\ \ \ \      }}}
      \hspace{5mm} 
      \putnode{t2}{t1}{15}{0}{\pscirclebox[doubleline=true]{\mbox{\ \ \ \ }}} 
      \psset{arrows=->} \ncline{t0}{t1} 
      \ncline{t1}{t2} 
      \putnode{l0}{t1}{7}{2}{\clazy} \nccurve[angleA=45, angleB=135, 
        ncurv=4, nodesep=-1]{t1}{t1} 
      \putnode{l1}{t1}{0}{8}{\acdr, \clazy} \nccurve[angleA=45,
        angleB=135, ncurv=3, nodesep=-1]{t2}{t2} 
      \putnode{l2}{t2}{0}{8}{\clazy}
    \end{pspicture}
}}
\newcommand{\dfaD}{%
  \scalebox{.7}{
    \psset{unit=1mm,nodesep=0mm,labelsep=0.5mm}
    \begin{pspicture}(2,-2)(14,8)
      \putnode{t0}{origin}{2}{0}{}
      \putnode{t1}{t0}{8}{0}{\pscirclebox[doubleline=true]{
          \mbox{\ \ \ \ }}}     
      \psset{arrows=->}    
      \ncline{t0}{t1}     
      \nccurve[angleA=45, angleB=135, ncurv=2, nodesep=-1]{t1}{t1} 
      \putnode{l1}{t1}{0}{8}{\acdr}
    \end{pspicture}
}}
The  NFA for \var{\Df{\length}{1}} is 
\nfaD\ and the final DFA is \dfaD.
This  expectedly says  that
for  a  demand  $\sigma_{\length}$,   the  liveness  of  the  argument
of \length\ is $\acdr^{*}$ (the spine of the list is traversed).
